---
title: "Data 550 Midterm Project - Wastewater data Reproducible Report"
author: "Akshay Deverakonda"
date: "`r Sys.Date()`"
output: html_document
--- 

```{r, set-chunk-opts, echo = FALSE}
library(knitr)
library(magick)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

This report runs several analyses on U.S. Centers for Disease Control and Prevention wastewater surveillance data.

```{r, load-data}
here::i_am("report.Rmd")

```

Analysis 1

A table showing for each state what the average change of the “ptc_15d” variable over the reporting periods included in this document is.

```{r, table}
ptc_15d_table <- readRDS(
  file = here::here("output/Analysis_1/table.rds")
)
print(ptc_15d_table)
```

Analysis 2 

A table showing the top 20 jurisdictions with highest average detection proportions

```{r}
top_20_table <- readRDS(
  file = here::here("output/Analysis_2/table.rds")
)
print(top_20_table)
```

Analysis 3

A scatterplot with the X axis being population levels of each wastewater treatment plant, and the Y axis will be the average of the detect_prop_15d values recorded for each population size. 

```{r}
img_3 <- image_read(here::here("Output/Analysis_3/plot.png"))
print(img_3)
```


Analysis 4

This script creates a bar chart summarizing "avg_detect_prop_15d" by season

```{r}
img_4 <- image_read(here::here("Output/Analysis_4/plot.png"))
print(img_4)
```

