---
title: "Data 550 Midterm Project - Wastewater data Reproducible Report"
author: "Akshay Deverakonda"
date: "`r Sys.Date()`"
output: html_document
--- 

```{r, setup, include=FALSE}
options(repos = c(CRAN = "https://cloud.r-project.org/"))
library(yaml)
config <- yaml::read_yaml("config.yml")  
knitr::opts_chunk$set(echo = TRUE)

```


```{r, set-chunk-opts, echo = FALSE}
install.packages("pacman")
pacman::p_load(config, knitr, magick)

```

This report runs several analyses on U.S. Centers for Disease Control and Prevention wastewater surveillance data.

```{r, load-data}
here::i_am("report.Rmd")

```


Analysis 1: A table showing for each state what the average change of the “ptc_15d” variable over the reporting periods included in this document.

```{r analysis_1, eval=config$include_analysis_1}



ptc_15d_table <- readRDS(
  file = here::here("output/Analysis_1/table.rds")
)
print(ptc_15d_table)
```

Analysis 2 - A table showing the top 20 jurisdictions with highest average detection proportions

```{r analysis_2, eval=config$include_analysis_2}


top_20_table <- readRDS(
  file = here::here("output/Analysis_2/table.rds")
)
print(top_20_table)
```

Analysis 3 - A scatterplot with the X axis being population levels of each wastewater treatment plant, and the Y axis will be the average of the detect_prop_15d values recorded for each population size. 

```{r analysis_3, eval=config$include_analysis_3}


img_3 <- image_read(here::here("Output/Analysis_3/plot.png"))
print(img_3)
```

Analysis 4 -This script creates a bar chart summarizing "avg_detect_prop_15d" by season


```{r analysis_4, eval=config$include_analysis_4}

img_4 <- image_read(here::here("Output/Analysis_4/plot.png"))
print(img_4)
```

